
```{r}
library(ggplot2)
library(broom.mixed)
library(dplyr)
library(rstatix)
library(readxl)
library(purrr)
library(dunn.test)
library(lmerTest)
library(lme4)
library(Matrix)
library(ggpubr)
library(MASS)
library(ez)
library(ARTool)
library(emmeans)
library(stargazer)
library(sjPlot)
library(autoReg)
library(broom)
library(glmnet)
library(mediation)
library(lavaan)
library(readr)
```
# Delay condition analysis
```{r}
df <- read_excel("../data/df_bm_g_crqa.xlsx")
df$condition <- factor(as.character(df$condition), levels = c("0ms", "500ms", "1000ms"))
df$participant <- factor(as.character(df$participant))
head(df)
```
## Body motion analysis
```{r}
# Perform z-score normalization
df <- df %>%
  mutate(avg_bm_z = scale(avg_bm))
```
### Average body movement grouped by delay
```{r}
# Summary statistics
stats_delay <- df %>%
  group_by(condition) %>%
  get_summary_stats(avg_bm_z, type = "common")
# Export to csv
#write.csv(stats_delay, "stats_results/summary_stats_body_motion.csv", row.names = FALSE)
#

# Open a PDF device
pdf("plots/boxplot_body_motion.pdf", width = 4, height = 4)

# Box plot
ggplot(df, aes(x=condition, y=avg_bm_z)) + geom_boxplot(outlier.shape=NA) +
  labs(x="Delay", y="Mean body motion")

dev.off()
```
### Linear main effect regression modeling
```{r}
fit.bm <- lmer(avg_bm_z ~ condition + (1|participant), data = df, REML = FALSE)
summary(fit.bm)
performance::icc(fit.bm)
fit.bm %>% anova()
# Extract the model results
sjPlot::tab_model(fit.bm)
tab_model(fit.bm, file="models/fit_bm.html")
# Extract the model results into a CSV file
tidy_fit <- tidy(fit.bm)
write.csv(tidy_fit, "../results/models/fit_bm_results.csv", row.names = FALSE)
```
## Gaze behavior analysis
```{r}
# Perform z-score normalization
df <- df %>%
  mutate(freq_face_z = scale(freq_face))
df <- df %>%
  mutate(time_face_z = scale(time_face))
df <- df %>%
  mutate(time_card_z = scale(time_card))
df <- df %>%
  mutate(freq_card_z = scale(freq_card))
head(df)
```

### Face
#### Satistics
```{r}
# Summary statistics
df %>%
  group_by(condition) %>%
  get_summary_stats(time_face_z, type = "common")
# Export to csv
#write.csv(stats_delay, "summary_stats_condition.csv", row.names = FALSE)
#
df %>%
  group_by(condition) %>%
  get_summary_stats(freq_face_z, type = "common")
#write.csv(stats_cq, "summary_stats_cq.csv", row.names = FALSE)

# Open a PDF device
pdf("plots/boxplot_looking_partner_t.pdf", width = 4, height = 4)
# Box plot
ggplot(df, aes(x=condition, y=time_face_z)) + geom_boxplot(outlier.shape=NA) +
  labs(x="Delay", y="Total time of looking-partner")
dev.off()

# Open a PDF device
pdf("../results/plots/boxplot_looking_partner_n.pdf", width = 4, height = 4)
# Box plot
ggplot(df, aes(x=condition, y=freq_face_z)) + geom_boxplot(outlier.shape=NA) +
  labs(x="Delay", y="Total number of looking-partner")
dev.off()
```

#### Time face Linear main effect regression modeling
```{r}
fit.tf <- lmer(time_face_z ~ condition + (1|participant), data = df, REML = FALSE)
summary(fit.tf)
performance::icc(fit.tf)
fit.tf %>% anova()
# Extract the model results
sjPlot::tab_model(fit.tf)
tab_model(fit.tf, file="models/fit_tf.html")
# Extract the model results into a CSV file
tidy_fit <- tidy(fit.tf)
write.csv(tidy_fit, "../results/models/fit_tf_results.csv", row.names = FALSE)
```
#### Frequency face Linear main effect regression modeling
```{r}
fit.ff <- lmer(freq_face_z ~ condition + (1|participant), data = df, REML = FALSE)
summary(fit.ff)
performance::icc(fit.ff)
fit.ff %>% anova()
# Extract the model results
sjPlot::tab_model(fit.ff)
tab_model(fit.ff, file="models/fit_ff.html")
# Extract the model results into a CSV file
tidy_fit <- tidy(fit.ff)
write.csv(tidy_fit, "../results/models/fit_ff_results.csv", row.names = FALSE)
```
### Card
#### Satistics
```{r}
# Summary statistics
df %>%
  group_by(condition) %>%
  get_summary_stats(time_card_z, type = "common")
# Export to csv
#write.csv(stats_delay, "summary_stats_condition.csv", row.names = FALSE)
#
df %>%
  group_by(condition) %>%
  get_summary_stats(freq_card_z, type = "common")
#write.csv(stats_cq, "summary_stats_cq.csv", row.names = FALSE)
```
#### Time card Linear main effect regression modeling
```{r}
fit.tc <- lmer(time_card_z ~ condition + cq + (1|participant), data = df, REML = FALSE)
summary(fit.tc)
performance::icc(fit.tc)
fit.tc %>% anova()
```
#### Freq card Linear main effect regression modeling
```{r}
fit.fc <- lmer(freq_card_z ~ condition + (1|participant), data = df, REML = FALSE)
summary(fit.fc)
performance::icc(fit.fc)
fit.fc %>% anova()
```
### Room
#### Satistics
```{r}
# Summary statistics
df %>%
  group_by(condition) %>%
  get_summary_stats(time_room, type = "common")
# Export to csv
#write.csv(stats_delay, "summary_stats_condition.csv", row.names = FALSE)
#
df %>%
  group_by(condition) %>%
  get_summary_stats(freq_room, type = "common")
#write.csv(stats_cq, "summary_stats_cq.csv", row.names = FALSE)
```
#### Time room Linear main effect regression modeling
```{r}
fit.tr <- lmer(time_room ~ condition + (1|participant), data = df, REML = FALSE)
summary(fit.tr)
performance::icc(fit.tr)
fit.tr %>% anova()
```
#### Freq room Linear main effect regression modeling
```{r}
fit.fr <- lmer(freq_room ~ condition + (1|participant), data = df, REML = FALSE)
summary(fit.fr)
performance::icc(fit.fr)
fit.fr %>% anova()
```
## Body movement coordination
### CRQA
#### %REC
```{r}
# Perform z-score normalization
df <- df %>%
  mutate(REC_z = scale(REC))
head(df)
```
```{r}
# Open a PDF device
pdf("../results/plots/boxplot_REC.pdf", width = 4, height = 4)
# Box plot
ggplot(df, aes(x=condition, y=REC_z)) + geom_boxplot(outlier.shape=NA) +
  labs(x="Delay", y="Coordination similarity (%REC)")
dev.off()
```

```{r}
fit.rec <- lmer(REC_z ~ condition + (1|participant), data = df, REML = FALSE)
summary(fit.rec)
performance::icc(fit.rec)
fit.rec %>% anova()
# Extract the model results
sjPlot::tab_model(fit.rec)
tab_model(fit.rec, file="../results/models/fit_rec.html")
```
#### %DET
```{r}
# Perform z-score normalization
df <- df %>%
  mutate(DET_z = scale(DET))

# Open a PDF device
pdf("../results/plots/boxplot_DET.pdf", width = 4, height = 4)
# Box plot
ggplot(df, aes(x=condition, y=DET_z)) + geom_boxplot(outlier.shape=NA) +
  labs(x="Delay", y="Coordination organization (%DET)")
dev.off()

fit.det <- lmer(DET_z ~ condition + (1|participant), data = df, REML = FALSE)
summary(fit.det)
performance::icc(fit.det)
fit.det %>% anova()
# Extract the model results
sjPlot::tab_model(fit.det)
tab_model(fit.det, file="../results/models/fit_det.html")
```
#### maxLine
```{r}
# Perform z-score normalization
df <- df %>%
  mutate(maxLine_z = scale(maxLine))

# Open a PDF device
pdf("../results/plots/boxplot_maxLine.pdf", width = 4, height = 4)
# Box plot
ggplot(df, aes(x=condition, y=maxLine_z)) + geom_boxplot(outlier.shape=NA) +
  labs(x="Delay", y="Coordination stability (maxLine)")
dev.off()

fit.maxl <- lmer(maxLine_z ~ condition + (1|participant), data = df, REML = FALSE)
summary(fit.maxl)
performance::icc(fit.maxl)
fit.maxl %>% anova()
# Extract the model results
sjPlot::tab_model(fit.maxl)
tab_model(fit.maxl, file="../results/models/fit_maxl.html")
```
## DCRP & Growth curve analysis (using linear mixed effect model or polynomial regression to capture the growth trajectory)
```{r}
df_drp <- read_csv("../data/df_dcrp.csv")
df_drp$condition <- factor(as.character(df_drp$condition), levels = c("0ms", "500ms", "1000ms"))
df_drp$ID <- factor(as.character(df_drp$ID))
head(df_drp)
```
### Perform GRA
```{r}
# centering time lag
df_drp = df_drp %>% 
  mutate(Lag = scale(X))
# normalization
df_drp = df_drp %>% 
  mutate(RR = scale(profile))
head(df_drp)
```

```{r}
fit.gra <- lmer(RR ~ poly(Lag, 2)*condition + (1 | ID), data = df_drp, REML = FALSE)
summary(fit.gra)
#plot(fit.gra)
performance::icc(fit.gra)
fit.gra %>% anova()
# Extract the model results
sjPlot::tab_model(fit.gra)
tab_model(fit.gra, file="../results/models/gra.html")
sjPlot::plot_model(fit.gra, type="pred", terms=c("Lag[all]", "condition"))
```


### Line Plot
```{r}
new <- df_drp %>%
  group_by(condition, X) %>%
  summarise(RR = mean(profile))
head(new)
```
```{r}
df_0 <- new[new["condition"] == "0ms", ]
# Open a PDF device
pdf("../results/plots/lineplot_RR_0ms.pdf", width = 4, height = 3)
ggplot(data=df_0, aes(x=X, y = RR))+geom_line(size=1.5)+ylim(0.17,0.24)+xlab("Lag")+ylab("RR")
dev.off()
```
```{r}
df_500 <- new[new["condition"] == "500ms", ]
pdf("../results/plots/lineplot_RR_500ms.pdf", width = 4, height = 3)
ggplot(data=df_500, aes(x=X, y = RR))+geom_line(size=1.5)+ylim(0.17,0.24)+xlab("Lag")+ylab("RR")
dev.off()
```
```{r}
df_1000 <- new[new["condition"] == "1000ms", ]
pdf("../results/plots/lineplot_RR_1000ms.pdf", width = 4, height = 3)
ggplot(data=df_1000, aes(x=X, y = RR))+geom_line(size=1.5)+ylim(0.17,0.24)+xlab("Lag")+ylab("RR")
dev.off()
```


